Signed-Rank Test

### 2024-03-19 examples/examples.qmd
update examples
updte

				<img class="postcard__img" src="https://picsum.photos/801/800" alt="Image Title" />	

@@

				  <li class="tag__item"><i class="fas fa-tag mr-2"></i></li>
					<li class="tag__item"><i class="fas fa-clock mr-2"></i></li>

@@

```{=html}
<div class="d-flex flex-column justify-content-center w-100 h-100">

	<div class="d-flex flex-column justify-content-center align-items-center">
		<h1 class="fw-light text-white m-0">Pure CSS Gradient Background Animation</h1>
		<div class="btn-group my-5">
			<a href="https://codepen-api-export-production.s3.us-west-2.amazonaws.com/zip/PEN/pyBNzX/1578778289271/pure-css-gradient-background-animation.zip" class="btn btn-outline-light" aria-current="page"><i class="fas fa-file-download me-2"></i> SOURCE CODE</a>
			<a href="https://codepen.io/P1N2O/full/pyBNzX" class="btn btn-outline-light">FULL SCREEN <i class="fas fa-expand ms-2"></i></a>
		</div>
		<a href="https://manuel.pinto.dev" class="text-decoration-none">
			<h5 class="fw-light text-white m-0">— Pen by Manuel Pinto —</h5>
		</a>
	</div>
</div>
</div>
```

>>>>

@@

						<a href="_blank"><i class="fas fa-play
						mr-2"></i>Twin Designs</a>
						<a href="_blank"><i class="fas fa-play
						mr-2"></i>Zero-Inflation Models</a>
						<a href="_blank"><i class="fas fa-play
						mr-2"></i>Longitudinal Invariance</a>

@@
